An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-29 abstract.tex
Updated the article

\begin{abstract}
The development of cyber-physical systems (CPS) is challenging due to the heterogeneity of the different subsystems. To assist in the development process, co-simulation can be used, where models of constituents of a CPS are coupled to jointly simulate the behavior of the full system. However, a trustworthy result of the co-simulation is only obtained if all of the simulation units are initialized correctly and in the correct order. In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU). The Functional Mock-up Interface specification specifies constraints to the initialization of variables in the scope of a single FMU. However, it does not consider the initialization of interconnected variables between instances of FMUs. Such interconnected variables place particular constraints on the initialization order of the FMUs.\\
The approach taken to calculate a correct initialization order is based on predicates from the specification and the topological ordering of both internal connections and interconnected variables. Circular dependencies between FMU variables are dismissed. %This approach has been compared to other already existing approaches for FMI initialization. 
The approach has been realized as a plugin for the open-source INTO-CPS Maestro 2 Co-simulation framework. It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application. The approach has also been directly tested against an established co-simulation algorithm generator implemented in Prolog.

\keywords{Co-simulation \and Initialization \and Topological ordering \and FMI}
\end{abstract}

>>>>

\begin{abstract}
The development of cyber-physical systems (CPS) is challenging due to the heterogeneity of the different subsystems. Co-simulation can be used to assist in the development process, where models of constituents of a CPS are coupled to simulate the behavior of the full system jointly. However, an accurate result of the co-simulation is dependent on the correct initialization of all the simulation units. In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU). The Functional Mock-up Interface specification specifies constraints to the initialization of variables in the scope of a single FMU. However, it does not consider the initialization of interconnected variables between instances of FMUs. Such interconnected variables place particular constraints on the initialization order of the FMUs.\\
The approach taken to calculate a correct initialization order is based on predicates from the FMI specification and the topological ordering of both internal connections and interconnected variables. The approach supports the initialization of algebraic loops using fixed point iteration.%  dependencies between FMU variables are dismissed. %This approach has been compared to other already existing approaches for FMI initialization. 
The approach has been realized as a plugin for the open-source INTO-CPS Maestro 2 Co-simulation framework. It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application.% The approach has also been directly tested against an established co-simulation algorithm generator implemented in Prolog.

\keywords{Co-simulation \and Initialization \and Algebraic loop \and Topological ordering \and FMI}
\end{abstract}

### 2020-06-29 conclusion.tex
Updated the article

\section{Concluding remarks}\label{sc:summary}
This work used a topological ordering based on the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The calculated initialization order is optimized to group similar variables to perform fewest possible operations.
This approach ensures absence of cycles between interconnected FMU variables by defining the criteria for valid co-simulation scenarios.
This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation algorithm generator and verifier implemented in Prolog using an integration.\\
Future work includes formally verifying the plugin, and its implementation of the algorithm used to calculate the topological ordering using the Logika framework.
Future work will also look into generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede, Peter Gorm Larsen and Claudio Gomes for providing valuable input to this paper and the developed plugin.

>>>>

\section{Concluding remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The calculated initialization order is optimized to group variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration. The approach does also discard all co-simulation scenarios which are not adhering to the law of convergence \ref{def:convergence}.
This approach can be combined with an arbitrary master algorithm to run the co-simulation. \\
The approach was realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
Future work will also look into the generation of a verification strategy for the whole Maestro 2 framework to explore how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

\paragraph*{\textbf{Acknowlegements.}}We would like to thank Stefan Hallerstede and Peter Gorm Larsen for providing valuable input to this paper and the developed plugin.

### 2020-06-29 introduction.tex
Updated the article

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}. The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently,
that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given interval of time. \\
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface describing how to communicate with each simulation unit. This interface can be used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time. \\
A typical co-simulation consists of three phases: Initialization, simulation, and teardown. This work concentrates on the first of these phases - the initialization phase. FMI specifies criteria for how an FMU shall be initialized. However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole. 
The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables. The precedence constraints make specific system configurations and initialization orders of a system invalid due to cyclic dependencies and dependencies among the interconnected variables. An appropriate order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem}. Circular dependencies are important to avoid in a co-simulation scenario since they reduces the ability of a co-simulation to converge \cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}.\\

This paper describes an approach for the initialization of an FMI-based co-simulation in linear time of the number of interconnected variables. The approach complies with the semantics of FMI and ensures the absence of cycles in the system. The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2). The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. Gomes et al. have created a co-simulation algorithm generator and verifier\cite{gomes_lucio_vangheluwe_2019} in Prolog an integration to this realization has been crated as a part of the plugin. This integration is used to verify the calculated initialization order against an already established method for calculating the initialization order.\\

The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2. Section \ref{sc:initilization} describes the approach taken to calculate the initialization order. This is followed by section \ref{sc:implementation}, where the realization of the approach is presented. Finally, section \ref{sc:summary} provides concluding remarks and describes future work.

>>>>

\section{Introduction}\label{sc:introduction}
Cyber-physical systems (CPS) are becoming ever more sophisticated, while market pressure shortens the available development time. One of the tools used to manage the increasing complexity of such systems is co-simulation since it addresses their various parts of heterogeneous nature. Co-simulation is a technique to combine multiple black-box simulation units to simulate/compute the behavior of the combined models as a discrete trace\cite{Kubler2000}. The simulation units, often developed independently from each other, are coupled using a master algorithm, also often developed independently, that communicates with each simulation unit via its interface. This interface comprises functions for setting/getting inputs/outputs, and computing the associated model behavior over a given time interval. \\
The Functional Mock-up Interface (FMI) standard \cite{Blochwitz2012, fmi_2019} is such an interface prescribing how to communicate with each simulation unit. The interface is used to connect different simulation units (called Functional Mock-up Units or FMUs) and exchange values between them and make them progress in time. \\

A typical co-simulation consists of three phases: Initialization, simulation, and teardown. This work concentrates on the first of these phases - the initialization phase. The FMI specification specifies criteria for how a single FMU shall be initialized. However, the FMI standard is not concerned with how a connected system of multiple FMUs should be correctly initialized as a whole. 
The way a system of multiple FMUs should be initialized and interacted with depends on each FMUs implementation and interconnections to other FMUs \cite{gomes_lucio_vangheluwe_2019}, since these place precedence constraints between the FMU variables. The precedence constraints between the variables can introduce algebraic loops, which places particular requirements on the initialization order since the algebraic loops require a particular initialization strategy to be applied to calculate the initial values of the variables in the algebraic loop\cite{Bastian2011a}. The order of initialization is vital for the correctness of the co-simulation \cite{Thule2018} because it ensures a variable is never read before it is set like the classical \textit{readers–writers problem} and to make sure that all initial values have stabilized at the start of the simulation.

\noindent Algebraic loops occur whenever there is an interconnected FMU variable that indirectly depends on itself. Algebraic loops introduce specific challenges in the co-simulation, and studies have shown that neglecting a loop can lead to a prohibitively high error in the co-simulation \cite{Kubler2000}. Other approaches for the generation of co-simulation algorithms have avoided co-simulation scenarios containing algebraic loops since their presence reduces the chance of obtaining a valid co-simulation result\cite{Amalio2016CheckingCo-simulation, BromanCompositionCo-Simulation}. This choice is motivated by the fact that not all co-simulation scenarios containing algebraic loops are valid since some algebraic loops have a divergent nature. However, experience has shown that valid co-simulation scenarios containing algebraic loops exist, and a well-established co-simulation framework should be able to handle these scenarios.

\textit{Contribution:} This paper describes an approach for calculating the initialization order of an FMI-based co-simulation in linear time of the number of interconnected variables. The approach complies with the semantics of FMI and support the initialization of algebraic loops between interconnected FMU variables and identifies divergent co-simulation scenarios. The approach does not put any constraints on choosing a master algorithm that should be used to carry out the simulation. This means that the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. The approach has been realized as a plugin to the co-simulation framework called INTO-CPS Maestro 2 (Maestro 2). \\
The realized plugin has been tested for various co-simulation scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial applications. 
Furthermore, the calculated initialization order is systematically verified by an established co-simulation Algorithm Generator and Verifier by Gomes et al. implemented in Prolog \cite{gomes_lucio_vangheluwe_2019}. \\

\textit{Structure:} The paper is structured as follows: Section \ref{sc:background} gives a brief background of the formalization of FMUs and Maestro 2. Section \ref{sc:initilization} describes the approach taken to calculate the initialization order. This is followed by section \ref{sc:implementation}, where the realization of the approach is presented. Finally, section \ref{sc:summary} provides concluding remarks and describes future work.
